Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-01 ms.tex
zorak

Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating source (stars, MSPs, SNe Ia, and black hole feedback) calculated for the average star formation history of galaxies containing a given black hole mass.  Again, Ia heating is suppressed in low mass galaxies because the Ia radius exceeds the nominal stagnation radius, with $r_{\rm Ia}/r_{\rm s}$ shown in Fig. ~\ref{fig:eta} (bottom panel).  MSP heating is again found to be negligible for all black hole masses.  The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind and Ia heating being dominant, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and $v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.  Only for the most massive galaxies $\Mbh\gsim 5\times 10^{8} \Msun$ does the lack of younger stellar populations significantly reduces the role of stellar wind heating.   Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.  Strikingly, {\it we find that galactic nuclei experiencing the same average star formation history as their host galaxies produce thermally stable flows across most black hole masses}.

@@

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {it Top Panel:} Sources contributing   to the heating rate of the CNM, $\vwO$, including stellar wind heating ({\it orange}), Ia supernovae ({\it green}), millisecond pulsars ({\it blue}), and compton heating ({\it pink}).  Each heating source varies with black hole mass $\Mbh$ due to the different
  average star formation history of galaxies of a given halo mass (see
  Appendix~\ref{app:windheat} for the detailed description). The total
  heating rate is shown in black. {\it Bottom Panel:} The
  ratio of the total heating rate ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the radiating cooling rate
  ($|\dot{q}_{\rm rad}|$) at the stagnation radius.  Dashed lines and red color show the thermally unstable region defined by $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| < 1$, for which the assumption of steady-state flow would be violated.  {\bf BDM: remove the red - its tacky and will vary based on core/cusp.  Draw a dashed line across at heating ratio of 1.  change y axis labels!  move stars label in top panel}}
\end{figure}

@@

The X-ray luminosities of galactic nuclei provide a powerful diagnostic of the SMBH accretion rates and how they vary across different galaxy properties and SMBH masses (e.g.,  \citealt{Ho08}  and references therein).  Figure \ref{fig:vwSources} shows that the heating associated with the average star formation history of a galaxy is approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.  For a fixed wind heating parameter, the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  This dependence, shown directly in Figure XXX, appears to contradict the observed behavior of the nuclear X-ray luminosities of quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Gallo+10, Miller+15}.

@@

@@

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Bottom panel:} Growth times $\Mbh/\Mdot$ in units
  of the Hubble time $\th$ for core ($\Gamma=0.1$, solid black) and
  cusp galaxies ($\Gamma=0.8$, dash-dotted black). These are calculated from
  equation~\ref{eq:tgrow_analytic} with parameters chosen for the
  average star formation history at each $\Mbh$. We also plot a lower
  bound on growth time for a themally stable flow (yellow) from
  equation~\eqref{eq:tgrow_min}.}
\end{figure}

>>>>

Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating source (stars, MSPs, SNe Ia, and black hole feedback) calculated for the average star formation history of galaxies containing a given black hole mass.  Again, Ia heating is suppressed in low mass galaxies because the Ia radius exceeds the nominal stagnation radius (bottom panel).  MSP heating is again found to be negligible for all black hole masses.  The younger stellar populations characterizing galaxies with $\Mbh\lsim 5\times 10^{8} \Msun$ results in stellar wind and Ia heating being dominant, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and $v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.  Only for the most massive galaxies $\Mbh\gsim 5\times 10^{8} \Msun$ does the lack of younger stellar populations significantly reduces the role of stellar wind heating.   Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.  Strikingly, {\it we find that galactic nuclei experiencing the same average star formation history as their host galaxies produce thermally stable flows across most black hole masses}.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {it Top Panel:} Sources contributing to the total heating rate of the CNM, $\vwO$ ({\it black}), including stellar wind heating ({\it orange}), Ia supernovae ({\it green}), millisecond pulsars ({\it blue}), and compton heating ({\it pink}).  Each heating source varies with black hole mass $\Mbh$ calculated for average star formation histories from
  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for details).  {\it Bottom Panel:} The
  ratio of the total heating rate ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the radiating cooling rate
  ($|\dot{q}_{\rm rad}|$) at the stagnation radius.  Dashed lines and red color show the thermally unstable region defined by $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| < 1$, for which the assumption of steady-state flow would be violated.  {\bf BDM: remove the red - its tacky and will vary based on core/cusp.  Draw a dashed line across at heating ratio of 1.  change y axis labels!  move stars label in top panel}}
\end{figure}

@@

@@

The X-ray luminosities of galactic nuclei provide a powerful diagnostic of the SMBH accretion rates and how they vary across different galaxy properties and SMBH masses (e.g.,  \citealt{Ho08}  and references therein).  Figure \ref{fig:vwSources} shows that the heating associated with the average star formation history of a galaxy is approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.  For a fixed wind heating parameter, the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).

This dependence is shown more directly in Figure \ref{fig:bh_growth}, where we plot the

appears to contradict the observed behavior of the nuclear X-ray luminosities of quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Gallo+10, Miller+15}.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Top panel:} Various critical values of the black hole accretion rate $\dot{M}$ in Eddington units as a function of black hole mass $M_{\bullet}$, shown separately for core ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$, dot-dashed lines).  Black lines show the accretion rate calculated from equation (\ref{eq:eddr}), according to the total stellar wind heating due to the average star formation histories from \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for details).  Green lines show the maximum accretion set by Ia supernovae blow-out (\ref{eq:eddr_Ia}).  Red lines show the Compton-regulated accretion rate (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum accretion rate for a thermally stable flow near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  {\it Bottom panel:} Growth times $\Mbh/\Mdot$ in units
  of the Hubble time $\th$ for each of the accretion rates shown in the top panel.}
\end{figure}

@@
